Apprentissage par renforcement inverse en cascadant classification et régression

### 2013-04-05 piot2012cascading_JFPDA/Cascading.tex
Version soumise à JFPDA2013

The objective criterion for success is the number of steps needed to attain the goal when starting from a state picked at random ; the lesser the better. We can see Fig.~\ref{fig:MountainCar} that the optimal policies for the rewards found by SCIRL and CSI very rapidly attain expert-level performance and outperform the optimal policy for the reward of RE and the classification policy. When very few samples are available, CSI does better than SCIRL (with such a low $p$-value for $n=10$, see Tab.~\ref{tab:mc}, the hypothesis that the mean performance is equal can be rejected); SCIRL catches up when more samples are available. Furthermore, CSI required very little engineering as we cascaded two off-the-shelf implementations whereas SCIRL used hand-tuned features and a custom classifier.
\begin{table}
	\begin{center}
		\begin{tabular}{cc}
		\toprule
			Number of expert samples & $p$-value\\
			\midrule
			$10$ & $4.5195\e{-14}$\\
			$30$ & $0.0131123$\\
			$100$ & $0.139975$\\
			$300$ & $0.893752$\\
		\bottomrule
		\end{tabular}
	\end{center}
        \caption{Kolmogorov–Smirnov mean equality test $p$-values for CSI and SCIRL on the mountain car. High values (>0.01) means that the hypothesis that the means are equal cannot be rejected.}
        \label{tab:mc}
\end{table}
\begin{figure}
  \includegraphics[width=\textwidth]{Exp11.pdf}
  \caption{Performance of various policies on the mountain car problem. This is the mean over 100 runs.}
  \label{fig:MountainCar}
\end{figure}

@@

Furthermore, the classifier whose results are diplayed here is the output of the first step of the algorithm. The classification performance is obviously not that good, this hints to the fact that our algorithm may be empirically more forgiving of classification errors than our theoretical bound lets us expect.
\begin{table}[ht]
	\begin{center}
		\begin{tabular}{cc}
		\toprule
			Number of expert samples & $p$-value\\
			\midrule
			$9$ & $0.193042$\\
			$49$ & $0.00178467$\\
			$100$ & $0.00178467$\\
			$225$ & $6.66654\e{-22}$\\
			$400$ & $3.70654\e{-36}$\\
		\bottomrule
		\end{tabular}
	\end{center}
        \caption{Kolmogorov–Smirnov mean equality test $p$-values for CSI and SCIRL on the highway simulator. High values (>0.01) means that the hypothesis that the means are equal cannot be rejected.}
        \label{tab:highway}
\end{table}
  \begin{figure}
   \subfigure[Mean performance over 100 runs on the Highway driving problem.]{\label{tutu}\includegraphics[width=.5\linewidth]{"Exp14"}}
   \subfigure[Zoom of Fig~\ref{tutu} showing the ranking of the three IRL algorithms.]{\includegraphics[width=.5\linewidth]{"Exp14_zoom"}}
  \caption{Results on the highway driving problem.}
  \label{fig:Highway}

>>>>

The objective criterion for success is the number of steps needed to attain the goal when starting from a state picked at random ; the lesser the better. We can see Fig.~\ref{fig:MountainCar} that the optimal policies for the rewards found by SCIRL and CSI very rapidly attain expert-level performance and outperform the optimal policy for the reward of RE and the classification policy. When very few samples are available, CSI does better than SCIRL (with such a low $p$-value for $n=10$, see Tab.~\ref{tab:mc}, the hypothesis that the mean performance is equal can be rejected); SCIRL catches up when more samples are available. Furthermore, CSI required very little engineering as we cascaded two off-the-shelf implementations whereas SCIRL used hand-tuned features and a custom classifier.
\begin{table}
	\begin{center}
		\begin{tabular}{cc}
		\toprule
			Number of expert samples & $p$-value\\
			\midrule
                        $ 10$ & $\mathbf{1.5e-12}$\\
                        $ 30$ & $3.8e-01$\\
                        $100$ & $1.3e-02$\\
                        $300$ & $7.4e-01$\\
                        \bottomrule
		\end{tabular}
	\end{center}
        \caption{Student or Welch test of mean equality (depending on wether a Bartlett test of variance equality succeeds) $p$-values for CSI and SCIRL on the mountain car. High values ($>1.0\e{-02}$) means that the hypothesis that the means are equal cannot be rejected. As highlighted here, the means are different when the algorithms are fed only $10$ expert samples in which case CSI outperforms SCIRL.}
        \label{tab:mc}
\end{table}
\begin{figure}
  \includegraphics[width=\textwidth]{Exp11.pdf}
  \caption{Performance of various policies on the mountain car problem. This is the mean over 100 runs.}
  \label{fig:MountainCar}
\end{figure}

@@

Furthermore, the classifier whose results are diplayed here is the output of the first step of the algorithm. The classification performance is obviously not that good, this hints to the fact that our algorithm may be empirically more forgiving of classification errors than our theoretical bound lets us expect.
\begin{table}[ht]
	\begin{center}
		\begin{tabular}{cc}
		\toprule
			Number of expert samples & $p$-value\\
			\midrule
                        $  9$ & $3.0e-01$\\
                        $ 49$ & $\mathbf{8.9e-03}$\\
                        $100$ & $\mathbf{1.8e-03}$\\
                        $225$ & $\mathbf{2.4e-05}$\\
                        $400$ & $\mathbf{2.0e-50}$\\
                        \bottomrule
		\end{tabular}
	\end{center}
        \caption{Student or Welch test of mean equality (depending on wether a Bartlett test of variance equality succeeds) $p$-values for CSI and SCIRL on the driving simulator. High values ($>1.0\e{-02}$) means that the hypothesis that the means are equal cannot be rejected. As highlighted here, the means are different from 49 samples on : CSI slightly but definitively outperforms SCIRL.}
        \label{tab:highway}
\end{table}
  \begin{figure}
   \subfigure[Mean performance over 100 runs on the Highway driving problem.]{\label{tutu}\includegraphics[width=.5\linewidth]{"Exp14"}}
   \subfigure[Zoom of Fig~\ref{tutu} showing the ranking of the three IRL algorithms.]{\includegraphics[width=.5\linewidth]{"Exp14_zoom"}}
  \caption{Results on the highway driving problem.}
  \label{fig:Highway}
